The interview is the main part of my project. And I want to show it in the
following order: 1. About how I found the interviwee family. 2. The demographic
structure of that family, and what their home looks like. 3. Their response to
my interview questions.
\subsection{How I found them}
The interviewee family is the host of my Airbnb house of my Chicago trip during
the Thanks Giving holiday. When I arrived their home, it was afternoon, and was
strongly snowing out side. I had nothing to do, so I chated with them, and found
they came from South Korean, and the hostess Ann (psudoname), whom I contacted
directly on Airbnb, was born in America, and had just graduated from 
University of Chicago last year. She is a singer and song writer now.
\subsection{Brief information about that family}
The family lives in a house in the suburban area of Chicago. Honestly, when I
first stepped into their home, I couldn't see difference from the ordinary
American homes, except a ink picture of mountain and river with Korean
Characters on it. Everything else is almost the same as other American
families. However, their home is not as clean as other American families. 
\par
There are four people in her family:her parents, her elder brother who is
working in Chicago, and herself. Also, her boy friend, who is a white boy, will
come to visit her occationally. Her parents immigranted to American thirty years
ago, and still have difficulty to speak good English. Ann told
me, when she was young, her parents had a small restaurant in the nearby
neighborhood. They're really friendly and gave me a lot help when I was in
Chicago.
\subsection{Their response to my interview question}
Now is their response to my interview questions.
\begin{itemize}
  \item First question I asked Ann, and her answer is yes.
  \item Second question, Ann told me, sometimes, she was really reluctant to
  work in her parents' restaurant because she had to do translation for her
  parents and needed to face a lot of unknown people, which would make her feel
  really shy. However, she also told me that she is now grateful for that
  experience because that made her open and confident. When she was not at her
  parents' resaturant, her brother would go over and do her jobs for their
  parents.
  \item Third question, 
\end{itemize}